\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks, colorlinks=true, urlcolor=resumeblue]{hyperref} % CHANGED: colored links, no underline
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{charter} % CHANGED: classic serif, more refined than Computer Modern
\input{glyphtounicode}

%----------COLOR-----------
\definecolor{resumeblue}{RGB}{26, 54, 93} % ADDED: dark navy accent color

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins — CHANGED: slightly less aggressive than before
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{0.8in}
\setlength{\footskip}{14pt} % CHANGED: 12pt -> 14pt to avoid underfull vbox warning

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting — CHANGED: added navy color to section title and rule
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{resumeblue}
}{}{0em}{}[\color{resumeblue}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% CHANGED: client name is now bold instead of italic small — more visual weight
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \normalsize\textit{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% CHANGED: custom font size for name, slightly less overwhelming than \Huge \scshape combo
\begin{center}
    {\fontsize{26}{28}\selectfont\scshape Luiz Felipe Diniz} \\ \vspace{3pt}
    \small Campinas, SP - Brazil $|$ \href{mailto:luizd97@gmail.com}{luizd97@gmail.com} $|$
    \href{https://www.linkedin.com/in/levin-diniz}{linkedin.com/in/levin-diniz} $|$
    \href{https://github.com/luizlevindiniz}{github.com/luizlevindiniz}
\end{center}


%-----------SUMMARY-----------
\section{Profile}
\small{
Full-stack Software Engineer with 3+ years building SaaS products and internal platforms using Ruby on Rails, React, Next.js, and TypeScript. Proven track record of delivering solutions for Brazilian and international clients through consulting engagements, with a strong background in product development and automation.
}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Codeminer42 (Consulting)}{Remote}
  {Full-stack Software Engineer}{Jan 2025 -- Present}

\resumeSubSubheading
  {Client: GLS.AI (US)}{}

\resumeItemListStart
  \resumeItem{Built an asynchronous document ingestion system using Active Storage, AWS S3, and Temporal to orchestrate batch uploads and background processing of 100+ documents/day, replacing manual handling workflows.}
  \resumeItem{Designed a multi-contact notification system supporting multiple emails and addresses per user, improving reliability and reducing the risk of missed system notifications.}
  \resumeItem{Created a foreclosure management dashboard using Ruby on Rails and Hotwire to support real estate-backed loan workflow tracking and operational monitoring.}
\resumeItemListEnd

\resumeSubSubheading
  {Client: Praia Para Todos}{}

\resumeItemListStart
  \resumeItem{Automated core operational workflows using Ruby on Rails and Active Admin, digitizing paper-based processes and saving dozens of hours of manual work per week.}
  \resumeItem{Integrated a third-party electronic signature system via webhooks to automate document approval pipelines and eliminate manual processing steps, reducing approval friction.}
  \resumeItem{Developed interactive forms and dynamic user interfaces using Hotwire (Turbo and Stimulus), improving the user experience across the platform.}
\resumeItemListEnd

\resumeSubSubheading
  {Client: Diversos Ingressos}{}

\resumeItemListStart
  \resumeItem{Architected a checkout state machine using Next.js and TypeScript to manage ticket purchasing flows, enhancing session consistency and seat reservation reliability.}
  \resumeItem{Improved application performance and SEO with hybrid Static Site Generation (SSG) and Server-Side Rendering (SSR), reducing page load latency and improving search engine discoverability.}
  \resumeItem{Integrated frontend applications with backend APIs to ensure real-time synchronization of purchasing sessions and ticket availability.}
\resumeItemListEnd

\resumeSubheading
  {Encora (Consulting)}{Remote}
  {Software Engineer Intern}{Apr 2024 -- Jan 2025}

\resumeSubSubheading
  {Client: BT Group (UK)}{}

\resumeItemListStart
  \resumeItem{Refactored and maintained production-grade web applications using React, TypeScript, and Styled-Components for large-scale telecommunications platforms, improving maintainability and UI consistency.}
  \resumeItem{Developed cross-platform desktop communication tools using Electron to support internal enterprise routines.}
  \resumeItem{Improved code reliability by implementing unit and integration test suites with Jest and React Testing Library, raising coverage to 90\%.}
\resumeItemListEnd

\resumeSubheading
  {BTG Pactual}{Hybrid}
  {Automation Intern}{Sep 2023 -- Feb 2024}

\resumeItemListStart
  \resumeItem{Built internal tools using React and FastAPI for equity analysts to access and analyze financial data, directly supporting trading desk operations in a production environment.}
  \resumeItem{Integrated AWS Athena to query and visualize large financial datasets, enabling faster access to daily asset information.}
  \resumeItem{Automated internal banking processes through AWS Lambda functions, scheduled jobs, and serverless data ingestion pipelines.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: TypeScript, Ruby, Python} \\
\textbf{Frontend}{: React, Next.js, Hotwire, Tailwind CSS} \\
\textbf{Backend}{: Ruby on Rails, Node.js, FastAPI} \\
\textbf{Testing}{: Jest, React Testing Library} \\
\textbf{Databases}{: PostgreSQL, Supabase} \\
\textbf{Cloud \& DevOps}{: AWS (S3, Lambda, Athena), Docker, GitHub Actions, Temporal} \\
\textbf{Spoken Languages}{: Portuguese (Native), English (Professional), Spanish (Conversational)}
}}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://parliapp.vercel.app/landing}{Parli} $|$ \emph{Next.js, TypeScript, Supabase, Stripe}}{}
\resumeItemListStart
\resumeItem{Released a multi-tenant SaaS platform for language tutors.}
\resumeItem{Implemented authentication, subscription billing, student management, and class scheduling features.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://g3ari.com.br}{G3A} $|$ \emph{Next.js, TypeScript, shadcn/ui}}{}
\resumeItemListStart
\resumeItem{Delivered a modern corporate website for a property regularization firm.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
  {Virtual State University of São Paulo (UNIVESP)}{São Paulo, Brazil}
  {B.Sc. in Computer Engineering}{}

\vspace{4pt}
\resumeSubheading
  {State University of Campinas (UNICAMP)}{Campinas, Brazil}
  {B.Sc. in Food Engineering}{}

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
