\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Luiz Felipe Diniz} \\ \vspace{1pt}
    \small Campinas, SP - Brazil $|$ \href{mailto:luizd97@gmail.com}{\underline{luizd97@gmail.com}} $|$
    \href{https://www.linkedin.com/in/levin-diniz}{\underline{linkedin.com/in/levin-diniz}} $|$
    \href{https://github.com/luizlevindiniz}{\underline{github.com/luizlevindiniz}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virtual State University of São Paulo (UNIVESP)}{São Paulo, Brazil}
      {Bachelor’s Degree in Computational Engineering}{July 2022 -- Present}
    \resumeSubheading
      {State University of Campinas (UNICAMP)}{Campinas, Brazil}
      {Bachelor’s Degree in Food Engineering}{March 2016 -- June 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Codeminer42}{Remote}
      {Software Developer}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developed the frontend checkout flow for a Brazilian ticketing platform using Next.js and TypeScript; the solution was featured in a  \href{https://blog.codeminer42.com/finite-state-machines-and-how-to-build-any-step-by-step-flow-in-react/}{\underline{post}} on the Codeminer42 Blog.}
        \resumeItem{Delivered a full-stack volunteer management system using Ruby on Rails, enabling a non-profit to coordinate 400+ volunteers and logistical operations across 10 coastal locations in Rio de Janeiro, significantly reducing paperwork and manual processes.}
        \resumeItem{Optimized loan-related processes for a US-based loan management firm, refining the core logic behind loan payoff calculations.}
        \resumeItem{Enhanced the UI of internal Codeminer projects using Tailwind CSS and Hotwire.}
      \resumeItemListEnd

    \resumeSubheading
      {Encora LLC}{Remote}
      {Software Developer}{Mar 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Developed frontend features for a major British telecommunications enterprise, leveraging React and TypeScript to build accessible interfaces for high-traffic user portals.}
        \resumeItem{Contributed to internal engineering initiatives while deepening expertise in technologies like CSS, HTML, and JavaScript.}
    \resumeItemListEnd

    \resumeSubheading
      {BTG Pactual Bank}{Hybrid}
      {Software Developer}{Aug 2023 -- Feb 2024}
      \resumeItemListStart
        \resumeItem{Built a dashboard application integrating React, TypeScript, and FastAPI for the derivatives trading team; implemented direct query interfaces via AWS Athena SDK to provide daily asset data.}
        \resumeItem{Designed and deployed AWS Lambda functions, automating the ingestion and normalization of datasets into internal bank systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\underline{\href{https://parliapp.vercel.app/landing}{Parli}} $|$ \emph{Next.js, TypeScript, Tailwind CSS, Stripe, Supabase}}{}
          \resumeItemListStart
            \resumeItem{Architected a comprehensive SaaS for language tutors using Next.js and Supabase. Integrated Stripe for payment processing and engineered a dashboard for student/class management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\underline{\href{https://fernandobeloto.com.br}{Fernando Belotto}} $|$ \emph{Next.js, TypeScript, Tailwind CSS}}{}
          \resumeItemListStart
            \resumeItem{Delivered a highly performant, SEO-optimized portfolio site for a client.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\underline{\href{https://g3ari.com.br}{G3A}} $|$ \emph{Next.js, Shadcn UI}}{}
          \resumeItemListStart
            \resumeItem{Developed a modern corporate interface for a property regularization firm utilizing Shadcn UI components for consistent design systems.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Python, Ruby, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: React, Next.js, Ruby on Rails, FastAPI, Tailwind CSS, Hotwire} \\
     \textbf{Cloud \& Tools}{: AWS (Lambda, Athena), Git, Docker, Supabase, Stripe Integration} \\
     \textbf{Spoken Languages}{: Portuguese (Native), English (Professional)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}